Differential invariant signatures for planar Lie group transformations of images

### 2020-11-02 paper/newpaper.tex
Tidy up of figures. Can be programatically generated now

It is natural to seek representations of objects that vary only with regard to shape change, rather than to any change in form. If the space of objects in denoted $M$ and the non-shape transformations form a group $\mathcal{G}$, then mathematically one seeks a way to study objects in $M / \mathcal{G}$. This could be done, for example, by transforming all objects to match a chosen target one by registration. Hence for the group of similarity transformations (rotation and reflection, translation, and scale), a Procrustes alignment~\cite{} will transform all of the shapes into the reference frame of one template example. However, analysis on these quotient spaces is rarely simple~\cite{}. An alternative option is to seek $\mathcal{G}$-invariant functions on $M$ and use the theory of invariants, which is what we consider here.

@@

\section{Differential invariants of $E(2)$ through tensor contraction}
While we avoid the use of tensors in most of this study, there is a notable exception to be made for the Euclidean transformation group $E(2)$. In this setting we can restrict ourselves to \emph{Cartesian tensors}, where we need make no distinction between covariance and contravariance, as they are equivalent; we therefore use subscript indices exclusively.

@@

The main observation is that in this setting, the $n^\text{th}$ order partial derivative operator $\partial^n / \partial_{x_{i_1}} \cdots \partial_{x_{i_n}}$ formally transforms as an $n$-tensor. \todo[inline]{Cite Florack et al, 1993} Because the product of a $p$-tensor and a $q$-tensor gives a $(p+q)$-tensor and contraction of a $p$-tensor yields a $(p-2)$-tensor, a complete contraction of a tensor of even rank formed as a product of terms of the form $\partial f / \partial_{i_1} \cdots \partial_{i_p}$ will give a Euclidean invariant.

For example, up to second derivatives, we have the following Euclidean invariants, expressed as tensor contractions:
\begin{align*}
  f &= f \\
  f_if_i &= f_x^2 + f_y^2 \\
  f_{ii} &= f_{xx}^2 + f_{yy}^2 \\
  f_{ij} f_{ij} &= f_{xx}^2 + 2f_{xy}^2 + f_{yy}^2 \\
  f_i f_j f_{ij} &= f_x^2 f_{xx} + 2f_x f_y f_{xy} + f_y^2 f_{yy}
\label{eq:se2}
\end{align*}

@@

\subsection{Signatures of $SA(2)$ and $A(2)$}
Recall that invariants of a supergroup are automatically invariants of any of
its subgroups. For example, invariants of $A(2)$ are automatically invariants of $SA(2)$, but not necessarily vice versa. Any of the partial transvectants found in Tables~\ref{tab:transvectants1} and~\ref{tab:transvectants2} are invariants of $SA(2)$ (as the determinant is $1$), but only up to scale factor ($\det A^{-r}$) of $A(2)$.

@@

\subsubsection{Moving on to $A(2)$, \ldots}
Using the same function as an example, 
\begin{figure}
\centering
\includegraphics[width=.45\textwidth]{Figs/f_transformed_A2.png}
\includegraphics[width=.45\textwidth]{Figs/A2_signature.png}
\caption{A sample $A(2)$ Transform and 3D signature.}
\label{fig:A2}
\end{figure}

@@

\subsection{The Special Euclidean Group $SE(2)$}

>>>>

It is natural to seek representations of objects that vary only with regard to shape change, rather than to any change in form. If the space of objects is denoted $M$ and the non-shape transformations form a group $\mathcal{G}$, then mathematically one seeks a way to study objects in $M / \mathcal{G}$. This could be done, for example, by transforming all objects to match a chosen target one by registration. Hence for the group of similarity transformations (rotation and reflection, translation, and scale), a Procrustes alignment~\cite{} will transform all of the shapes into the reference frame of one template example. However, analysis on these quotient spaces is rarely simple~\cite{}. An alternative option is to seek $\mathcal{G}$-invariant functions on $M$ and use the theory of invariants, which is what we consider here.

@@

\section{Differential invariants of E(2) through tensor contraction}
While we avoid the use of tensors in most of this study, there is a notable exception to be made for the Euclidean transformation group $E(2)$. In this setting we can restrict ourselves to \emph{Cartesian tensors}, where we need make no distinction between covariance and contravariance as they are equivalent. We therefore use subscript indices exclusively.

@@

The main observation is that in this setting, the $n^\text{th}$ order partial derivative operator $\partial^n / \partial_{x_{i_1}}\cdots \partial_{x_{i_n}}$ formally transforms as an $n$-tensor. \todo[inline]{Cite Florack et al, 1993} Because the product of a $p$-tensor and a $q$-tensor gives a $(p+q)$-tensor and contraction of a $p$-tensor yields a $(p-2)$-tensor, a complete contraction of a tensor of even rank formed as a product of terms of the form $\partial^p f / \partial_{x_{i_1}} \cdots \partial_{x_{i_p}}$ will give a Euclidean invariant.

For example, up to second derivatives, we have the following Euclidean invariants, expressed as tensor contractions:
\begin{align*}
  f &= f \\
  f_if_i &= f_x^2 + f_y^2 \\
  f_{ii} &= f_{xx} + f_{yy} \\
  f_{ij} f_{ij} &= f_{xx}^2 + 2f_{xy}^2 + f_{yy}^2 \\
  f_i f_j f_{ij} &= f_x^2 f_{xx} + 2f_x f_y f_{xy} + f_y^2 f_{yy}
\label{eq:se2}
\end{align*}

@@

\subsection{Signatures of SA(2) and A(2)}
Recall that invariants of a supergroup are automatically invariants of any of
its subgroups. For example, invariants of $A(2)$ are automatically invariants of $SA(2)$, but not necessarily vice versa. Any of the partial transvectants found in Tables~\ref{tab:transvectants1} and~\ref{tab:transvectants2} are invariants of $SA(2)$ (as the determinant is $1$), but only up to scale factor ($\det A^{-r}$) of $A(2)$.

@@

\subsubsection{Moving on to A(2), \ldots}
Using the same function as an example, 
\begin{figure}
\centering
\includegraphics[width=.45\textwidth]{Figs/f_transformed_A2.png}
\includegraphics[width=.45\textwidth]{Figs/A2_signature.png}
\caption{A sample $A(2)$ Transform and 3D signature.}
\label{fig:A2}
\end{figure}

@@

\subsection{The Special Euclidean Group SE(2)}
